Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'

### 2023-08-02 stats/magnet.Rmd
edit manuscript figures and corresponding saves

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(psych) # corr.test
library(brms) # modeling
library(tidybayes) # modeling
library(ggpubr) # stat_cor 
library(corrplot) # corr plot
library(apaTables) # as name says
library(cocor) # compare correlations
library(magrittr) # extract list elements

@@

```{r plot_cor_ci}
cor_ci <- cor_matrix %>% 
  filter(Correlation != "ToM x Perspective-taking") %>% 
  mutate(Correlation = fct_relevel(Correlation, "Magnet x Perspective-taking", "Magnet x ToM", "Tango x Perspective-taking", "Tango x ToM", "Tango x Magnet")) %>%
  ggplot(., aes(x=Correlation, y=r, ymin=lower, ymax=upper)) +
  geom_pointrange(color = "#005555", size = 0.8, linewidth = 1) +
  scale_y_continuous(limits = c(-1, 1), breaks = seq(-1, 1, 0.25)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("") +
  coord_flip() +
  theme(axis.title.x = element_text(face="italic"))

@@

```{r modelplot}
modelplot <- magnet_draws %>% 
  mutate(
    includes_zero = ifelse(predictor == "Age (scaled)", TRUE, FALSE)
  ) %>%
  ggplot(., aes(x = estimate, y = predictor, fill = includes_zero)) +
 tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_alpha = 0.5) +
    labs(x = "Posterior estimate when predicting TANGO mean", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("#006c66", "#EBECEC")) +
  coord_cartesian(expand = TRUE, xlim = c(-0.6, 0.4), ylim = c(1.5, 3.5)) +
  theme_classic()

@@

```{r arrange_plot}
arrangedplot <- ggarrange(
  cor_ci, 
  modelplot, 
  ncol = 2, 
  labels = c("A", "B")
)

saveRDS(arrangedplot, file = "../saves/magnet_arrangedplot.rds")
ggsave("../figures/magnet_arrangedplot.png", width = 6, height = 2, scale = 1.75, bg = "white")
```

@@

saveRDS(williams_tom, "../saves/williams_tom.rds")

@@

saveRDS(williams_perspective, "../saves/williams_perspective.rds")
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(psych) # corr.test
library(brms) # modeling
library(tidybayes) # modeling
library(ggpubr) # stat_cor 
library(corrplot) # corr plot
library(apaTables) # as name says
library(cocor) # compare correlations
library(magrittr) # extract list elements
library(cowplot) # ggdraw, draw_image, plot_grid

@@

```{r plot_cor_ci}
cor_ci <- cor_matrix %>% 
  filter(Correlation != "ToM x Perspective-taking") %>% 
  mutate(Correlation = fct_relevel(Correlation, "Magnet x Perspective-taking", "Magnet x ToM", "Tango x Perspective-taking", "Tango x ToM", "Tango x Magnet")) %>%
  ggplot(., aes(x=Correlation, y=r, ymin=lower, ymax=upper)) +
  geom_pointrange(color = "black", size = 0.8, linewidth = 1) +
  scale_y_continuous(limits = c(-1, 1), breaks = seq(-1, 1, 0.25)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("") +
  coord_flip() +
  theme(axis.title.x = element_text(face="italic"))

@@

```{r modelplot}
magnet_draws <- readRDS("../saves/magnet_draws.rds")

modelplot <- magnet_draws %>% 
  mutate(
    includes_zero = ifelse(predictor == "Age (scaled)", TRUE, FALSE)
  ) %>%
  ggplot(., aes(x = estimate, y = predictor, fill = includes_zero)) +
 tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "darkgrey", slab_alpha = 0.9) +
    labs(x = "Posterior estimate TANGO mean", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("darkgrey", "#EBECEC")) +
  coord_cartesian(expand = TRUE, xlim = c(-0.6, 0.4), ylim = c(1.5, 3.5)) +
  theme_classic()

@@

@@

saveRDS(williams_tom, "../saves/magnet_williams_tom.rds")

@@

saveRDS(williams_perspective, "../saves/magnet_williams_perspective.rds")
```

```{r arrange_plot}
procedure_png <- ggdraw() + draw_image("../figures/procedure.png")
cor_ci <- readRDS(file = "../saves/magnet_cor_ci.rds")
modelplot <- readRDS(file = "../saves/magnet_modelplot.rds")

magnet_plot <- ggarrange(NULL, 
          procedure_png, 
          cor_ci, 
          modelplot, 
          NULL, 
          ncol = 5, 
          labels = c("A", "", "B", "C", ""),
          widths = c(1, 16, 18, 13, 1.5)
          )

saveRDS(magnet_plot, file = "../saves/magnet_plot.rds")
ggsave("../figures/magnet_plot.png", width = 10, height = 2, scale = 1.4, bg = "white")
ggsave("../figures/magnet_plot.pdf", width = 10, height = 2, scale = 1.4, bg = "white")

# alternative positioning: procedure on top, cor left below, model right below
# ggarrange(procedure_png, 
#           NULL, 
#           
#           ggarrange(
#             cor_ci, 
#             modelplot, 
#             NULL, 
#             ncol = 3, 
#             labels = c("B", "C", ""), 
#             widths = c(12, 10, 2)
#           ), 
#           
#           nrow = 3,
#           heights = c(11, 1, 9), 
#           labels = c("A", ""), 
#           align = "h"
#           )
# 
# # saveRDS(magnet_plot, file = "../saves/magnet_plot.rds")
# ggsave("../figures/magnet_plot2.png", width = 8, height = 5, scale = 1.2, bg = "white")
```

### 2023-08-02 stats/supplements_gaussianprocess.Rmd
edit manuscript figures and corresponding saves

write.csv(mgp_triallevel, "../saves/mgp_triallevel.csv", quote = F, row.names = F)
saveRDS(mgp_triallevel, "../saves/mgp_triallevel.rds")
```

@@

write.csv(mgp_aggregated, "../saves/mgp_aggregated.csv", quote = F, row.names = F)
saveRDS(mgp_aggregated, "../saves/mgp_aggregated.rds")
```

>>>>

write.csv(mgp_triallevel, "../saves/lifespan_mgp_triallevel.csv", quote = F, row.names = F)
saveRDS(mgp_triallevel, "../saves/lifespan_mgp_triallevel.rds")
```

@@

write.csv(mgp_aggregated, "../saves/lifespan_mgp_aggregated.csv", quote = F, row.names = F)
saveRDS(mgp_aggregated, "../saves/lifespan_mgp_aggregated.rds")
```

### 2023-08-02 supplements/supplements.Rmd
edit manuscript figures and corresponding saves

>>>>

# Lifespan
## Participants
```{r lifespan_sample, include = T, out.width = "100%"}
lifespan_sample <- readRDS("../saves/lifespan_sample.rds")

lifespan_table <- lifespan_sample %>% 
  mutate(
    n = str_glue_data(., "{n_total} ({n_females} female)"), 
    `Age range` = str_glue_data(., "{age_min} - {age_max}"), 
  ) %>% 
  rename(
    `Age group` = age_group,
    `Age SD` = age_sd, 
    `Age mean` = age_mean
  ) %>% 
  select(`Age group`, n, `Age mean`, `Age range`, `Age SD`)

apa_table(lifespan_table)
```

# Computational cognitive model 
## Imprecision by target position

(ref:figlab1) **Gaze funnel for adult sample with higher trial number**.
```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
knitr::include_graphics("../figures/gazefunnel_adults.pdf")
```
